``Don't tell me what it is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics

### 2015-04-14 manuscript.tex
Updates from ShareLaTeX

 \documentclass[conference]{IEEEtran}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\bstctlcite{IEEEexample:BSTcontrol}
\usepackage[table]{xcolor}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.9}
\usepackage{picture}
\newcommand{\kw}[1]{\textit{#1}}
\newcommand{\quart}[4]{\begin{picture}(50,3)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{flushend}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

@@

\begin{document}
  \title{``Don't tell me what is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}

@@

\subsection{Spectral Learning using WHERE}
The algorithm uses WHERE to recursively cluster the input data to identify subsets in the training data that a test instance can learn from. WHERE is a spectral learner which uses the FastMap heuristic to estimate the first principal component. It then recursively partitions the data into two halves along the median point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.

@@

\begin{figure}[htbp!]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
\begin{enumerate}
\item Find the two most distant points in a given population; say {\em east} and {\em west}. 
\item Draw an axis of length $c$ between the poles. 
\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
\item Using the median $x$ value, divide the population.
\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
\end{enumerate}

@@

Formally, WHAT can be considered as an instance based  learning scheme. And that's beacuse it builds a set of recommendations based on a given test case based on the clusters formed at the training stage. This is unlike a model based approach, which would have used a model to do the same~\cite{xomo}.
\\\hline
\end{tabular}
\caption{Inside WHAT}\label{fig:what}
\end{figure}

@@

The performance prediction data set was obtained from~\cite{}. The data set contains six examples of real world configurable systems: \kw{Apache}, \kw{LLVM}, \kw{x264}, \kw{Berkeley DB (written in C and Java}, and \kw{SQLite}. The systems have different characteristics, different implementation languages, and different configuration mechanisms. The data set is a collection of all possible configurations (with SQLITE being a exception with only 4653 configurations). We performed a 5-fold cross validation study on this data set.

@@

In addition to the above, we rank the different variants of the planning scheme to identify the best approach. We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks. It works as follows: A list of treatments \textit{l} is sorted by the median score. The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division. A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different. If so, Skott-Knott then recurses on each division.

@@

\section{Experimental Results}
\begin{figure}[!t]
  \centering
\begin{minipage}{0.5\textwidth}
\renewcommand{\baselinestretch}{}
{\bf \scriptsize Ant:}

{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 &     Baseline &    0.03  &  0.0 & \quart{0}{0}{0}{62} \\
    \hline  2 & $0.25$, Prune=50\% &    0.15  &  0.09 & \quart{4}{6}{7}{62} \\
    \hline  3 & $0.5$, Prune=50\% &    0.25  &  0.1 & \quart{12}{6}{14}{62} \\
    \hline  4 &     $0.25$ &    0.34  &  0.05 & \quart{18}{4}{20}{62} \\
    4 &   $0.25$, weight &    0.36  &  0.08 & \quart{18}{5}{21}{62} \\
    4 & $0.75$, Prune=50\% &    0.41  &  0.13 & \quart{21}{8}{24}{62} \\
    \hline  5 &    $0.5$, weight &    0.46  &  0.18 & \quart{24}{12}{27}{62} \\
    5 &      $0.5$ &    0.53  &  0.15 & \quart{27}{10}{32}{62} \\
    \hline  6 &     $0.75$ &    0.64  &  0.17 & \quart{34}{11}{39}{62} \\
    6 &   $0.75$, weight &    0.73  &  0.17 & \quart{38}{11}{45}{62} \\
    \hline \end{tabular}\\}

{\bf \scriptsize Camel}

{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
1 &   Baseline &    0.16  &  0.03 & \quart{0}{3}{1}{111} \\
1 &   $0.25$ &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
1 & $0.25$, weight &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
\hline  2 & $0.25$, Prune=50\% &    0.22  &  0.06 & \quart{5}{8}{9}{111} \\
\hline  3 &    $0.5$ &    0.25  &  0.1 & \quart{3}{14}{13}{111} \\
3 &  $0.5$, weight &    0.26  &  0.14 & \quart{7}{19}{14}{111} \\
\hline  4 & $0.5$, Prune=50\% &    0.32  &  0.16 & \quart{10}{21}{22}{111} \\
\hline  5 & $0.75$, weight &    0.38  &  0.19 & \quart{14}{25}{30}{111} \\
5 &   $0.75$ &    0.4  &  0.12 & \quart{23}{16}{32}{111} \\
\hline  6 & $0.75$, Prune=50\% &    0.47  &  0.15 & \quart{30}{19}{42}{111} \\
\hline \end{tabular}}\\

{\bf \scriptsize Ivy}

    {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
        \arrayrulecolor{darkgray}
        \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
        1 &     Baseline &    0.06  &  0.0 & \quart{0}{0}{0}{79} \\
        \hline  2 & $0.25$, Prune=50\% &    0.14  &  0.04 & \quart{4}{3}{6}{79} \\
        \hline  3 & $0.5$, Prune=50\% &    0.2  &  0.06 & \quart{9}{5}{11}{79} \\
        \hline  4 & $0.75$, Prune=50\% &    0.27  &  0.14 & \quart{10}{12}{17}{79} \\
        \hline  5 &     $0.25$ &    0.41  &  0.06 & \quart{27}{5}{29}{79} \\
        5 &   $0.25$, weight &    0.42  &  0.06 & \quart{27}{6}{30}{79} \\
        \hline  6 &    $0.5$, weight &    0.55  &  0.11 & \quart{35}{9}{41}{79} \\
        6 &      $0.5$ &    0.57  &  0.09 & \quart{37}{7}{43}{79} \\
        \hline  7 &   $0.75$, weight &    0.61  &  0.08 & \quart{42}{7}{46}{79} \\
        7 &     $0.75$ &    0.62  &  0.04 & \quart{46}{3}{47}{79} \\
        \hline \end{tabular}}\\

{\bf \scriptsize Jedit}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 &   Baseline &    0.05  &  0.0 & \quart{0}{0}{0}{75} \\
      \hline  2 & $0.25$, Prune=50\% &    0.11  &  0.05 & \quart{2}{4}{4}{75} \\
      \hline  3 & $0.5$, Prune=50\% &    0.16  &  0.1 & \quart{3}{8}{8}{75} \\
      \hline  4 &   $0.25$ &    0.2  &  0.08 & \quart{10}{6}{11}{75} \\
      4 & $0.25$, weight &    0.21  &  0.1 & \quart{7}{8}{12}{75} \\
      \hline  5 & $0.75$, Prune=50\% &    0.32  &  0.15 & \quart{15}{11}{21}{75} \\
      5 &  $0.5$, weight &    0.33  &  0.05 & \quart{19}{4}{22}{75} \\
      5 &    $0.5$ &    0.34  &  0.18 & \quart{18}{14}{23}{75} \\
      \hline  6 &   $0.75$ &    0.56  &  0.2 & \quart{27}{16}{40}{75} \\
      6 & $0.75$, weight &    0.56  &  0.26 & \quart{29}{20}{40}{75} \\
      \hline \end{tabular}}\\
\end{minipage}
\end{figure}
\begin{figure}
\begin{minipage}{0.5\textwidth}
  \renewcommand{\baselinestretch}{}
{\bf \scriptsize Log4j}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $0.5$, Prune=50\% &    0.1  &  0.06 & \quart{1}{11}{5}{172} \\
      1 & $0.25$, Prune=50\% &    0.11  &  0.04 & \quart{1}{8}{7}{172} \\
      1 & $0.25$, weight &    0.1  &  0.03 & \quart{3}{6}{5}{172} \\
      1 &  $0.5$, weight &    0.1  &  0.13 & \quart{0}{24}{5}{172} \\
      1 &   Baseline &    0.11  &  0.04 & \quart{0}{7}{7}{172} \\
      1 &   $0.25$ &    0.12  &  0.06 & \quart{1}{11}{9}{172} \\
      \hline  2 &    $0.5$ &    0.15  &  0.09 & \quart{3}{17}{14}{172} \\
      2 & $0.75$, Prune=50\% &    0.15  &  0.05 & \quart{9}{9}{14}{172} \\
      2 & $0.75$, weight &    0.17  &  0.22 & \quart{9}{40}{18}{172} \\
      2 &   $0.75$ &    0.22  &  0.16 & \quart{14}{30}{27}{172} \\
      \hline \end{tabular}}\\

{\bf \scriptsize Lucene}

{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 & $0.25$, weight &    0.03  &  0.03 & \quart{0}{4}{1}{148} \\
    1 &  $0.25$ &    0.05  &  0.04 & \quart{1}{6}{4}{148} \\
    \hline  2 &   $0.5$ &    0.09  &  0.09 & \quart{6}{13}{10}{148} \\
    2 & $0.25$, Prune=50\% &    0.09  &  0.03 & \quart{7}{5}{10}{148} \\
    2 &  Baseline &    0.1  &  0.01 & \quart{10}{2}{12}{148} \\
    2 & $0.5$, weight &    0.14  &  0.06 & \quart{10}{9}{18}{148} \\
    \hline  3 & $0.5$, Prune=50\% &    0.19  &  0.08 & \quart{21}{12}{25}{148} \\
    \hline  4 & $0.75$, weight &    0.23  &  0.15 & \quart{22}{23}{31}{148} \\
    4 &  $0.75$ &    0.26  &  0.1 & \quart{27}{15}{36}{148} \\
    4 & $0.75$, Prune=50\% &    0.28  &  0.13 & \quart{30}{19}{39}{148} \\\hline \end{tabular}}\\

{\bf \scriptsize Poi}

{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 & $0.25$, Prune=50\% &    0.09  &  0.15 & \quart{0}{9}{3}{62} \\
    1 &     Baseline &    0.09  &  0.05 & \quart{2}{3}{3}{62} \\
    1 & $0.5$, Prune=50\% &    0.12  &  0.13 & \quart{1}{8}{5}{62} \\
    \hline  2 &     $0.25$ &    0.24  &  0.3 & \quart{5}{19}{13}{62} \\
    2 &   $0.25$, weight &    0.25  &  0.32 & \quart{4}{20}{14}{62} \\
    \hline  3 & $0.75$, Prune=50\% &    0.37  &  0.45 & \quart{4}{29}{21}{62} \\
    3 &    $0.5$, weight &    0.49  &  0.5 & \quart{9}{32}{29}{62} \\
    \hline  4 &     $0.75$ &    0.53  &  0.47 & \quart{16}{30}{32}{62} \\
    4 &      $0.5$ &    0.53  &  0.28 & \quart{18}{18}{32}{62} \\
    4 &   $0.75$, weight &    0.61  &  0.43 & \quart{22}{27}{37}{62} \\
    \hline \end{tabular}}  \\

{\bf \scriptsize Velocity}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $0.25$ &    0.08  &  0.03 & \quart{0}{4}{1}{140} \\
      1 & $0.25$, weight &    0.09  &  0.05 & \quart{0}{7}{3}{140} \\
      \hline  2 & Baseline &    0.13  &  0.04 & \quart{6}{6}{9}{140} \\
      \hline  3 & $0.5$ &    0.16  &  0.09 & \quart{9}{13}{13}{140} \\
      3 & $0.25$, Prune=50\% &    0.17  &  0.04 & \quart{13}{6}{15}{140} \\
      3 & $0.5$, weight &    0.19  &  0.09 & \quart{12}{13}{18}{140} \\
      \hline  4 & $0.5$, Prune=50\% &    0.22  &  0.11 & \quart{15}{16}{22}{140} \\
      4 & $0.75$, weight &    0.25  &  0.1 & \quart{19}{15}{27}{140} \\
      4 & $0.75$ &    0.28  &  0.2 & \quart{19}{30}{31}{140} \\
      4 & $0.75$, Prune=50\% &    0.28  &  0.09 & \quart{24}{13}{31}{140} \\
      \hline \end{tabular}}\\

{\bf \scriptsize Xalan}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $0.75$, weight &    0.31  &  0.14 & \quart{0}{31}{13}{170} \\
      1 & $0.25$, weight &    0.32  &  0.1 & \quart{2}{22}{15}{170} \\
      1 &   $0.25$ &    0.32  &  0.06 & \quart{13}{14}{15}{170} \\
      \hline  2 &    $0.5$ &    0.34  &  0.11 & \quart{6}{25}{20}{170} \\
      2 &   Baseline &    0.36  &  0.13 & \quart{4}{30}{24}{170} \\
      2 &  $0.5$, weight &    0.35  &  0.12 & \quart{6}{28}{22}{170} \\
      2 & $0.5$, Prune=50\% &    0.36  &  0.12 & \quart{11}{27}{24}{170} \\
      2 & $0.25$, Prune=50\% &    0.38  &  0.1 & \quart{13}{23}{29}{170} \\
      2 & $0.75$, Prune=50\% &    0.37  &  0.21 & \quart{2}{47}{27}{170} \\
      2 &   $0.75$ &    0.38  &  0.17 & \quart{6}{39}{29}{170} \\
      \hline \end{tabular}}
 \end{minipage}  
   \end{figure}

% \section{Discussion}
% \section{Threats to validity}
% \section{Conclusion}
% \section*{Acknowledgements}

\bibliography{References}{}
\bibliographystyle{IEEEtran}
\end{document}

>>>>

 \documentclass[conference]{IEEEtran}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\bstctlcite{IEEEexample:BSTcontrol}
\usepackage[table]{xcolor}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.9}
\usepackage{picture}
\newcommand{\kw}[1]{\textit{#1}}
\newcommand{\quart}[4]{\begin{picture}(75,6)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{flushend}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

@@

\begin{document}
  \title{``Don't tell me what it is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}

@@

\subsection{Spectral Learning using WHERE}
The algorithm uses WHERE to recursively cluster the input data to identify subsets in the training data that a test instance can learn from. WHERE is a spectral learner which uses the FastMap heuristic to estimate the first principal component. It then recursively partitions the data into two halves along the Medianian point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.

@@

\begin{figure}[htbp!]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
\begin{enumerate}
\item Find the two most distant points in a given population; say {\em east} and {\em west}. 
\item Draw an axis of length $c$ between the poles. 
\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
\item Using the Medianian $x$ value, divide the population.
\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
\end{enumerate}

@@

Formally, WHAT can be considered as an instance based  learning scheme. And that's beacuse it builds a set of recommendations based on a given test case based on the clusters forMedian at the training stage. This is unlike a model based approach, which would have used a model to do the same~\cite{xomo}.
\\\hline
\end{tabular}
\caption{Inside WHAT}\label{fig:what}
\end{figure}

@@

The performance prediction data set was obtained from~\cite{}. The data set contains six examples of real world configurable systems: \kw{Apache}, \kw{LLVM}, \kw{x264}, \kw{Berkeley DB (written in C and Java}, and \kw{SQLite}. The systems have different characteristics, different implementation languages, and different configuration mechanisms. The data set is a collection of all possible configurations (with SQLITE being a exception with only 4653 configurations). We perforMedian a 5-fold cross validation study on this data set.

@@

In addition to the above, we rank the different variants of the planning scheme to identify the best approach. We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks. It works as follows: A list of treatments \textit{l} is sorted by the Medianian score. The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division. A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different. If so, Skott-Knott then recurses on each division.

@@

\section{Experimental Results}
\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{_figs/Histogram}
\caption{Caption}
\label{fig:bugs}
\end{figure}

\begin{figure*}[!t]

\noindent\begin{minipage}{0.5\textwidth}
  {\scriptsize \textbf{Ant}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
      1 &     Base &    0.13  &  0.03 & \quart{0}{1}{1}{48}\\
      \hline  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.05 & \quart{3}{3}{4}{48}\\
      \hline  3 & 0.5, weighting,  iP=50\% &    0.26  &  0.06 & \quart{6}{3}{8}{48}\\
      \hline  4 &     0.25 &    0.3  &  0.1 & \quart{7}{6}{10}{48}\\
      4 &   0.25&    0.3  &  0.08 & \quart{8}{4}{10}{48}\\
      \hline  5 & 0.75, weighting,  iP=50\% &    0.42  &  0.13 & \quart{13}{7}{17}{48}\\
      5 &      0.5 &    0.43  &  0.1 & \quart{14}{6}{17}{48}\\
      5 &    0.5&    0.43  &  0.1 & \quart{15}{5}{17}{48}\\
      \hline  6 &   0.75&    0.64  &  0.19 & \quart{22}{10}{29}{48}\\
      6 &     0.75 &    0.63  &  0.08 & \quart{26}{4}{28}{48}\\
      \hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Camel}\\}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   Base &    0.15  &  0.05 & \quart{0}{4}{1}{75}\\
\hline  2 &   0.25 &    0.18  &  0.06 & \quart{1}{5}{4}{75}\\
  2 & 0.25&    0.2  &  0.06 & \quart{2}{5}{6}{75}\\
  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.04 & \quart{4}{3}{6}{75}\\
\hline  3 &  0.5&    0.25  &  0.1 & \quart{6}{9}{10}{75}\\
  3 &    0.5 &    0.26  &  0.12 & \quart{6}{11}{11}{75}\\
  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.11 & \quart{10}{9}{13}{75}\\
\hline  4 & 0.75&    0.39  &  0.16 & \quart{19}{13}{22}{75}\\
  4 &   0.75 &    0.42  &  0.17 & \quart{15}{15}{25}{75}\\
  4 & 0.75, weighting,  iP=50\% &    0.42  &  0.1 & \quart{20}{9}{25}{75}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & 0.25, weighting,  iP=50\% &    0.15  &  0.04 & \quart{0}{2}{0}{55}\\
\hline  2 &     Base &    0.16  &  0.0 & \quart{1}{0}{1}{55}\\
  2 &     0.25 &    0.18  &  0.06 & \quart{1}{4}{2}{55}\\
  2 &   0.25&    0.2  &  0.06 & \quart{1}{4}{3}{55}\\
\hline  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.08 & \quart{7}{5}{9}{55}\\
\hline  4 &      0.5 &    0.33  &  0.11 & \quart{8}{7}{12}{55}\\
  4 &    0.5&    0.37  &  0.09 & \quart{10}{6}{14}{55}\\
\hline  5 & 0.75, weighting,  iP=50\% &    0.38  &  0.16 & \quart{12}{10}{15}{55}\\
\hline  6 &   0.75&    0.56  &  0.08 & \quart{25}{5}{27}{55}\\
  6 &     0.75 &    0.57  &  0.12 & \quart{25}{7}{27}{55}\\[-0.01cm]
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Jedit}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   Base &    0.06  &  0.01 & \quart{0}{0}{0}{64}\\
\hline  2 & 0.25&    0.08  &  0.06 & \quart{0}{4}{1}{64}\\
  2 &   0.25 &    0.09  &  0.05 & \quart{0}{3}{2}{64}\\
\hline  3 & 0.25, weighting,  iP=50\% &    0.12  &  0.08 & \quart{1}{5}{4}{64}\\
\hline  4 &  0.5&    0.16  &  0.09 & \quart{4}{6}{6}{64}\\
  4 &    0.5 &    0.17  &  0.09 & \quart{4}{6}{7}{64}\\
\hline  5 & 0.5, weighting,  iP=50\% &    0.22  &  0.11 & \quart{8}{8}{10}{64}\\
  5 & 0.75&    0.26  &  0.18 & \quart{9}{12}{13}{64}\\
\hline  6 &   0.75 &    0.38  &  0.31 & \quart{11}{21}{21}{64}\\
  6 & 0.75, weighting,  iP=50\% &    0.41  &  0.17 & \quart{17}{12}{24}{64}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Log4j}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   Base &    0.06  &  0.03 & \quart{0}{4}{4}{139}\\
\hline  2 & 0.25&    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
  2 &   0.25 &    0.09  &  0.06 & \quart{4}{8}{8}{139}\\
  2 & 0.25, weighting,  iP=50\% &    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
  2 &    0.5 &    0.1  &  0.07 & \quart{4}{10}{10}{139}\\
\hline  3 &  0.5&    0.12  &  0.03 & \quart{10}{4}{12}{139}\\
\hline  4 & 0.75&    0.13  &  0.11 & \quart{10}{15}{14}{139}\\
  4 &   0.75 &    0.13  &  0.06 & \quart{12}{9}{14}{139}\\
  4 & 0.5, weighting,  iP=50\% &    0.13  &  0.06 & \quart{10}{8}{14}{139}\\
\hline  5 & 0.75, weighting,  iP=50\% &    0.19  &  0.11 & \quart{17}{15}{22}{139}\\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Lucene}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &  0.25 &    0.05  &  0.02 & \quart{1}{4}{3}{188}\\
  1 & 0.25&    0.05  &  0.04 & \quart{0}{7}{3}{188}\\
\hline  2 &   0.5 &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
  2 & 0.25, weighting,  iP=50\% &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
  2 & 0.5&    0.08  &  0.05 & \quart{5}{10}{9}{188}\\
\hline  3 & 0.5, weighting,  iP=50\% &    0.1  &  0.03 & \quart{9}{6}{13}{188}\\
  3 &  Base &    0.1  &  0.03 & \quart{7}{6}{13}{188}\\
\hline  4 & 0.75, weighting,  iP=50\% &    0.13  &  0.09 & \quart{9}{18}{19}{188}\\
  4 &  0.75 &    0.15  &  0.08 & \quart{13}{16}{23}{188}\\
  4 & 0.75&    0.15  &  0.11 & \quart{11}{21}{23}{188}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Poi}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
      \arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &     Base &    0.1  &  0.03 & \quart{0}{2}{1}{61}\\
\hline  2 & 0.25, weighting,  iP=50\% &    0.14  &  0.1 & \quart{0}{6}{4}{61}\\
\hline  3 &   0.25&    0.18  &  0.14 & \quart{4}{9}{6}{61}\\
  3 &     0.25 &    0.19  &  0.11 & \quart{4}{7}{7}{61}\\
  3 & 0.5, weighting,  iP=50\% &    0.2  &  0.19 & \quart{4}{13}{8}{61}\\
\hline  4 & 0.75, weighting,  iP=50\% &    0.26  &  0.2 & \quart{8}{13}{12}{61}\\
  4 &      0.5 &    0.28  &  0.2 & \quart{6}{14}{13}{61}\\
  4 &    0.5&    0.33  &  0.22 & \quart{10}{14}{16}{61}\\
\hline  5 &     0.75 &    0.47  &  0.22 & \quart{18}{14}{26}{61}\\
  5 &   0.75&    0.46  &  0.11 & \quart{22}{7}{25}{61}\\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Synapse}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & Base &    0.15  &  0.0 & \quart{1}{0}{1}{44}\\
  1 & 0.5, weighting,  iP=50\% &    0.15  &  0.08 & \quart{1}{4}{1}{44}\\
  1 & 0.25, weighting,  iP=50\% &    0.17  &  0.08 & \quart{0}{4}{2}{44}\\
\hline  2 & 0.75, weighting,  iP=50\% &    0.21  &  0.08 & \quart{1}{4}{4}{44}\\
  2 & 0.25 &    0.23  &  0.18 & \quart{2}{9}{5}{44}\\
  2 & 0.25&    0.23  &  0.11 & \quart{2}{5}{5}{44}\\
\hline  3 & 0.5&    0.38  &  0.19 & \quart{7}{10}{12}{44}\\
  3 &  0.5 &    0.42  &  0.27 & \quart{6}{14}{14}{44}\\
\hline  4 & 0.75 &    0.5  &  0.39 & \quart{12}{20}{19}{44}\\
  4 & 0.75&    0.56  &  0.25 & \quart{17}{12}{22}{44}\\
\hline \end{tabular}}
\end{minipage}
